---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>",
fig.path = "man/figures/README-",
out.width = "100%"
)
```

# roblog

The goal of roblog is to provide helpers for authors of blog posts and tech notes on rOpenSci blog.

## Installation

``` r
remotes::install_github("ropenscilabs/roblog")
```


## (R) Markdown templates

If you want to execute code, use the R Markdown template. If not, use a Markdown template.

The helpers will create an untitled file with the template. Do not forget to save it.

### R Markdown template

Either

* Use the RStudio addin

* Select the template via File > New File > R Markdown > From Template

* Run `roblog::ro_blog_post_rmd()`

### Markdown template

Either

* Use the RStudio addin

* Run `roblog::ro_blog_post_md()`


## Lint

`ro_lint_md()` to be run on the path to your blog post (rendered, not the Rmd) to identify some potential problems and enforce: the use of complete alternative descriptions for image, of relative links to rOpenSci website, of Hugo shortcodes for tweets, of lower camelCase for rOpenSci name.


```{r lint}
path1 <- system.file(file.path("examples", "bad-no-alt.md"),
                                         package = "roblog")
roblog::ro_lint_md(path1)

path2 <- system.file(file.path("examples", "bad-no-alt2.md"),
                                         package = "roblog")
roblog::ro_lint_md(path2)

path3 <- system.file(file.path("examples", "allgood.md"),
                                         package = "roblog")
roblog::ro_lint_md(path3)
```

## How to prepare your pull request

You'll need to fork https://github.com/ropensci/roweb2 and create a branch. You can either use your usual workflow for that, or use [`usethis` helpers](https://usethis.r-lib.org/articles/articles/pr-functions.html), see below.

* Create the fork and check it out locally:

```r
usethis::create_from_github("ropensci/roweb2")
```

* Create a branch

```r
usethis::pr_init(branch = "mypost")
```
* Work locally (adding your post)

* Open the PR

```r
usethis::pr_push()
```
* Get feedback and use it

* Get changes from GitHub to local (e.g. Stef made a suggestion in the PR review and you accepted it)

```r
usethis::pr_pull()
```

* Get local changes to GitHub (e.g. you updated a paragraph and improved a figure from your laptop)

```r
usethis::pr_push
```
