---
title: "Create your author metadata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{author-file-guidance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

You'll need to create a file with your information (name, online presence) if you haven't already got one under [roweb2/content/authors](https://github.com/ropensci/roweb2/tree/master/content/authors).

## Why?

[Example of post, see clickable author name](https://ropensci.org/blog/2018/06/08/rprofile-julia-silge/).

[Example author page](https://ropensci.org/authors/kelly-obriant/).

```{r}
details::details(readLines("https://raw.githubusercontent.com/ropensci/roweb2/master/content/authors/kelly-obriant/_index.md"), summary = "Author metadata file", lang = "yaml")

```

The author metadata is the occasion to add links to your online presence, very good for future interactions (keywords: personal branding).

## How to?

Either

* Call the add-in from RStudio,

* Or run `roblog::ro_blog_post_author()` in RStudio,

* Or [copy-paste from the source file](https://github.com/ropenscilabs/roblog/blob/master/inst/templates/author-name.md).

