---
title: "Create your author metadata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{author-file-guidance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

You'll need to create a file with your information (name, online presence) if you haven't already got one under [roweb2/content/authors](https://github.com/ropensci/roweb2/tree/master/content/authors).

## Why?

The author metadata is the occasion to add links to your online presence, very good for future interactions (keywords: personal branding).

[Example of post, see clickable author name](https://ropensci.org/blog/2018/06/08/rprofile-julia-silge/).

[Example author page](https://ropensci.org/authors/kelly-obriant/).

```{r, echo = FALSE}
details::details(readLines("https://raw.githubusercontent.com/ropensci/roweb2/master/content/authors/kelly-obriant/_index.md"), summary = "Author metadata file", lang = "yaml")
```

## How to?

### Create the file

Either

* Call the add-in "rOpenSci Author" from RStudio,

* Or run `roblog::ro_blog_post_author()` in RStudio,

* Or copy-paste the text below (hover, a copy-paste button will appear at the top-right corner of the shaded area).

```{r, echo = FALSE}
library("magrittr")
yaml::read_yaml(system.file("templates", "author-name.md",
                  package="roblog")) %>% 
  yaml::as.yaml() %>%
  glue::glue_collapse("\n") -> x

glue::glue("```yaml\n----\n{x}---\n```")%>%
  knitr::asis_output()
```

### Save the file

In your fork of the website, under content/authors/, create a folder corresponding to your slugified name -- look at [other folder names](https://github.com/ropensci/roweb2/tree/master/content/authors) to get an idea. Save your author file as `_index.md` under this folder. E.g.:

* Kelly O'Briant in `content/authors/kelly-obriant/_index.md`,

* Stefanie Butland in `content/authors/stefanie-butland/_index.md`,

* Maëlle Salmon in `content/authors/maëlle-salmon/_index.md`.

