---
title: "Check your post"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{checks-guidance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Checklist

```{r, echo = FALSE}
library("magrittr")
read.csv(system.file("checklists", "submission-checklist.csv",
                  package="roblog"),
         header = FALSE,
         stringsAsFactors = FALSE) %>% 
  .[,1] %>%
  gluedown::md_task() -> x

glue::glue("````markdown\n{x}\n````") %>% 
  knitr::asis_output()
```

## Linting

Functions to be run on the path to your blog post (rendered, not the Rmd) 

`ro_lint_md()` should identify some potential problems and enforce: the use of complete alternative descriptions for image, of relative links to rOpenSci website, of Hugo shortcodes for tweets, of lower camelCase for rOpenSci name.

`ro_check_urls()` will identify possibly broken URLs.

```{r lint}
path1 <- system.file(file.path("examples", "bad-no-alt.md"),
                                         package = "roblog")
roblog::ro_lint_md(path1)
roblog::ro_check_urls(path1)
```
