---
title: "Write a post from R Markdown"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rmd-guidance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## A workflow suggestion

* Create a new R project (RStudio project for instance) in a dedicated folder e.g. `MyPost/`.

* Use the template (See following section) to create a  `index.Rmd` at the root of that folder.

* Work in that folder until you feel it's ready for submission. Then [refer to the submission guidance](articles/pr-guidance.html).

> Knitting the Rmd will generate both .html and .md files. Please do not include the html in your pull request to roweb2.

## Start from the template

Either

* Use the RStudio addin,

* Or select the template via File > New File > R Markdown > From Template in RStudio,

* Or run `roblog::ro_blog_post_rmd()` in RStudio,

* Or copy-paste the text below (hover, a copy-paste button will appear at the top-right corner of the shaded area).

```{r, echo = FALSE}
library("magrittr")
readLines(system.file("rmarkdown", "templates", "ropensci-blog-post", "skeleton", "skeleton.Rmd",
                  package="roblog")) %>% 
  glue::glue_collapse(sep = "\n") -> x

glue::glue("````markdown\n{x}\n````") %>% 
  knitr::asis_output()
```

